### 2017-05-31 paper.tex
Merging and editing abstract and author summary

\section*{Abstract}

\fixme{61}{Write abstract}

>>>>

\begin{abstract}

\noindent
Lessons take significant effort to build,
and even more effort to maintain.
The collaborative code development methods pioneered by the open source community
offer a way forward,
allowing us to create lessons which are open,
accessible,
and conntinually updated and improved by a community of contributors.
This paper provides ten simple rules that can help others create sustainable lessons.

\end{abstract}
